Model LF

### 2022-09-24 max_dp endogen stød.Rmd
lavet plots

```{r, echo=FALSE}
wage_trim_00 = S_model$simulation$wage_trim
dp_person_00 = S_model$simulation$dp_person
max_dp_00 = S_model$simulation$max_dp
stat_tilpas_00 = S_model$simulation$stat_tilpas
stat_reg_00= S_model$simulation$stat_tilpas
tilpas_pr_00 = S_model$simulation$tilpas_pr
wage_gap1_00 = S_model$simulation$wage_gap1
wage_ds_tt_00 = S_model$simulation$wage_ds_tt

@@

plot(yk_ds_01w, col= "red"); lines(yk_ds_01, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

 shock_part_model = TIMESERIES(shock_part_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_max_dp_model = TIMESERIES(shock_max_dp_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

plot(yk_ds_02, col= "red"); lines(yk_ds_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red"));
grid()

@@

plot(wage_ds_t_02, col= "red"); lines(wage_ds_t_01, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_gap_02, col= "red"); lines(wage_gap_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(max_dp_02, col= "red"); lines(max_dp_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

  shock_part_model = TIMESERIES(shock_part_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_max_dp_model = TIMESERIES(shock_max_dp_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_1_model = TIMESERIES(shock_1_model_shock+1 ,START=c(2014,2),  FREQ='Q')

@@

plot(ik_03, col= "red"); lines(ik_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_ds_t_03, col= "red"); lines(wage_ds_t_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

>>>>

```{r, echo=FALSE}
wage_trim_00 = S_model$simulation$wage_trim
dp_person_00 = S_model$simulation$dp_person
max_dp_00 = S_model$simulation$max_dp
stat_tilpas_00 = S_model$simulation$stat_tilpas
stat_reg_00= S_model$simulation$stat_tilpas
tilpas_pr_00 = S_model$simulation$tilpas_pr
wage_gap1_00 = S_model$simulation$wage_gap1
wage_ds_t_00 = S_model$simulation$wage_ds_t

@@

plot(yk_ds_01w, col= "red"); lines(yk_ds_01, col = "blue"); 
legend("top",legend=c("scenario 1", "Scenario 1w"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(yk_ds_01w, col= "red"); lines(yk_ds_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

 shock_part_model = TIMESERIES(shock_part_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_max_dp_model = TIMESERIES(shock_max_dp_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

plot(yk_ds_02, col= "red"); lines(yk_ds_01w, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red"));
grid()

@@

plot(wage_ds_t_02, col= "red"); lines(wage_ds_t_01w, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(max_dp_02, col= "red"); lines(max_dp_01w, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

  shock_part_model = TIMESERIES(shock_part_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_max_dp_model = TIMESERIES(shock_max_dp_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_1_model = TIMESERIES(shock_1_model_shock+1 ,START=c(2014,2),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

plot(wage_ds_t_03, col= "red"); lines(wage_ds_t_02, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

```{r}
plot((yk_ds_02 / yk_ds_00), ylim= c(0.95,1.03), col= "red");
lines((yk_ds_01w / yk_ds_00), col= "blue");
lines((yk_ds_01 / yk_ds_00), col= "green");
lines((yk_ds_03 / yk_ds_00), col= "orange")
legend("top", legend=c(""),
       lty=c(1),lwd=c(2),bty="n", col = c("red"));
grid()
```
